Analysis of Turkey's Trade with Selected Countries

### 2018-12-22 Draft/PresentationDraft.Rmd
.

@@

```{r}
glimpse(export_quantity_dataset)

@@

```{r}

@@

```{r}
glimpse(export_jTable)
```

@@

```{r}
glimpse(export_jTableMELTED)
```

>>>>

The purpose of the analysis is to understand the Turkey's trade Statistics for two way and with ten important countries.

Describe Turkey's the trade deficit with the country,year and product dimensions. Try to clear which factors effects deficit in trade, and is there relation deficit and other financials.

A clear understanding of the data to see if we can locate useful insights about which products and countries will remain the deficit and wich of them will be strategic for Turkey

@@

```{r, fig.align='center'}
glimpse(export_quantity_dataset)

@@

```{r, fig.align='center'}

@@

```{r, fig.align='center'}
glimpse(export_jTable)
```

@@

```{r, fig.align='center'}
glimpse(export_jTableMELTED)
```
